---
title: "Prescipt - Freebies"
output: html_document
date: "2022-09-27"
---

```{r setup, include=FALSE}
library(bigrquery)
library(dplyr)
library(DBI)
library(tidyverse)
library(magrittr)
library(fastDummies)
library(zoo)
library(lubridate)
```

When running the algorithm remember following!

- Edit the extraction paths so it fits your procedure. The bottom part of each flair script, as well as in the very bottom (Can be done with search and replace - CTRL + F)
- Put the file "training_data_algorithm_r72_newnegative" in every folder for each site
- Manually download positions from Campaign meister and save under the name "pos". Save in the same folder as the script.
- Change Date subset in line 139 and 140 so it fits current and last month
- ATM in the voonix data pulled from Big Query, we do not have that many clicks included
- To run RALPH - IF IT IS NOT THE FIRST SCRIPT RUN - position yourself on line 373 by clicking on the line. Then click "Run" -> "Run all chunks below" (This is important! Otherwise you will
  the big query extract once again) 

_______________________________________________________________________________

OVERALL DATA FLOW AND PROCESS

# Loading training data (Regression)

```{r}
training_data <- read.csv("training_data_algorithm_r72_newnegative.csv")
```

# Adjusting variables (Regression)

```{r}
# Selecting variables to include

# No positions = 21 and removing NA scores. In addition for the algorithm to work on lists with maybe only 12 or 18 pos, then assigning 4 categories of positions.

training_data %<>% mutate(Position = replace_na(Position, 21)) %>% mutate(Position = case_when(Position < 6 ~ "high",
                                                                                          Position > 5 & Position < 16 ~ "middle",
                                                                                          Position > 15 & Position < 21 ~ "low",
                                                                                          Position > 20 ~ "no pos")) %>% na.omit()

# Positions and new as dummy variable

training_data <- dummy_cols(training_data, select_columns = "Position")

training_data <- dummy_cols(training_data, select_columns = "new")

# Removing the original above variables to avoid multicollinarity.

training_data %<>% select(!(c(new, Position)))

# Indexing for removing names and to add them later. 

training_data$index <- 1:nrow(training_data)

new_index <- training_data[, c("name", "index")]

training_data %<>% select(!(name)) 
```

# Creating model (Regression)

```{r}
# Setting seed for same results

set.seed(2200)

# Creating the actual linear model.

lm_new <- lm(score ~ . - index, training_data)

# Summary to check R^2 and importance/weighing of variables
summary(lm_new)
```

# Loading Voonix data from Big Query (Voonix)

```{r}
con <- dbConnect(
  bigrquery::bigquery(),
  project = "casinomeister-302312",
  dataset = "CoverageMapDB",
  billing = "casinomeister-302312"
)

con
```

```{r}
sql <- "SELECT DISTINCT

CAST((date) AS DATE) AS Date,

adve_name,

sitename,

media,



SUM(ftd) AS FTD,

SUM(cpa_count) AS CPA,

SUM(clicks) AS Clicks,

SUM(signups) AS Signups,

SUM(rev_income) AS REV_income,

SUM(cpa_income) AS CPA_income,

SUM(extra_fee) AS Extra_fee



FROM `master-casino-stats.voonix_stats.monthly202*` 

WHERE DATE(date) > CURRENT_DATE() + INTERVAL -2 MONTH

GROUP BY  Date, adve_id, adve_name, sitename, media



--Order by 1 desc"

## SQL Language

voonix <- dbGetQuery(con, sql)

options(scipen = 999)
```

# REMEBER TO CHANGE THE DATE SUBSET!

```{r}
prev_month <- voonix %>% subset(Date == "2022-12-01") %>% select(!(Date)) %>% as.data.frame() 
current_month <- voonix %>% subset(Date == "2023-01-01")%>% select(!(Date)) %>% as.data.frame()
voonix <- full_join(prev_month, current_month, by = c("adve_name", "sitename", "media"))


voonix[is.na(voonix)] <- 0

# Adding the two months together
voonix <- transform(voonix, FTD = FTD.x + FTD.y)
voonix <- transform(voonix, CPA = CPA.x + CPA.y)
voonix <- transform(voonix, Clicks = Clicks.x + Clicks.y)
voonix <- transform(voonix, Signups = Signups.x + Signups.y)
voonix <- transform(voonix, REV_income = REV_income.x + REV_income.y)
voonix <- transform(voonix, CPA_income = CPA_income.x + CPA_income.y)
voonix <- transform(voonix, Extra_fee = Extra_fee.x + Extra_fee.y)

# Removing .x and .y variables
voonix %<>% select(!(c("FTD.x", "FTD.y", "CPA.x", "CPA.y", "Clicks.x", "Clicks.y", "Signups.x", "Signups.y", "REV_income.x", "REV_income.y", "CPA_income.x", "CPA_income.y", "Extra_fee.x", "Extra_fee.y")))

voonix$adve_name <- gsub("Luckom", "luckcom", voonix$adve_name, fixed = TRUE)
```

# Calculating variables C.FTD.., SU.FTD.., Total.income, click_value (Voonix)

```{r}
voonix %<>% mutate(REV_income = case_when(REV_income < 0 ~ 0,
                             TRUE ~ REV_income))

voonix %<>% mutate(C.FTD.. = FTD/Clicks) %>% mutate(SU.FTD.. = FTD/Signups) %>% mutate(Total.income = REV_income + CPA_income + Extra_fee)

# Creating click_value variable
voonix %<>% mutate(Clicks = case_when(Clicks == 0 ~ FTD,
                             TRUE ~ Clicks))

voonix$click_value <- voonix$Total.income / voonix$Clicks

# Removing redundant variables
voonix_add <- voonix

voonix %<>% select(!(c(Total.income, REV_income, CPA_income, Extra_fee, Signups)))

# Inf = 0

voonix[voonix == "Inf"] <- 0

# Renaming variables

voonix <- rename(voonix, Advertiser = adve_name)

```

# Removing non-active media (Voonix)

```{r}
voonix <- subset(voonix, media!="Legacy" & media!="email" & media!="Fallback" & media!="casinoeagle" & media!="Facebook BH" & media!="SEO" & media!="Google Ads" & media!="SMS")
```


# Getting wordpress data from BigQuery (Wordpress)

```{r}
sql2 <- "SELECT DISTINCT

siteid,

post_date_gmt,

closedStatus,

casinoID

FROM `casinomeister-302312.CoverageMapDB.wordpress`"

wordpress <- dbGetQuery(con, sql2)

wordpress$casinoID <- gsub("luckom", "luckcom", wordpress$casinoID, fixed = TRUE)
wordpress$casinoID <- gsub("sisu-3972", "sisu", wordpress$casinoID, fixed = TRUE)

```

_____________________________________________

Bad payers
- Get Outstanding Report from Finance, save it as beneath (outstanding_report)
- Download CSV of Lime filtered on Operators and adding the "Date established"
- Download Operator list and Brand list from lime! (Save files as: Operators & Brands)

```{r}
bad_payers <- read.csv("outstanding_report.csv")
```

```{r}
# Selecting relevant variables

bad_payers %<>% rename(Operator = Name)

# Removing text after "-" in string
bad_payers$Operator <- gsub("-.*","", bad_payers$Operator)
bad_payers$Operator <- gsub("TH.*","", bad_payers$Operator)

# Removing leading and trailing whitespace
bad_payers$Operator <- trimws(bad_payers$Operator)
```

```{r}
# Renaming variables

bad_payers <- rename(bad_payers, operator = Operator)
bad_payers <- rename(bad_payers, m1 = X0.30.days) 
bad_payers <- rename(bad_payers, m2 = X31.60.days)
bad_payers <- rename(bad_payers, m3 = X..60.days)

bad_payers$m1 <- as.numeric(gsub(",","",bad_payers$m1))
bad_payers$m2 <- as.numeric(gsub(",","",bad_payers$m2))
bad_payers$m3 <- as.numeric(gsub(",","",bad_payers$m3))

```

# Getting the Operators creation date for the dataset 

```{r}
operators <- read.csv("Operators.csv")
```

```{r}
operators %<>% select(c(Company.name, Date.established))

operators <- rename(operators, operator = Company.name)
operators <- rename(operators, established = Date.established)

# Making established as date
operators$established[operators$established == ""] <- "1/1/2020"

operators$established <- as.Date(operators$established, format = "%m/%d/%Y")

# Getting current date and calculating age in days
operators$today <- Sys.Date()

operators$age_days <- operators$today - operators$established

# Defining whether they are new or not
operators %<>% mutate(new = case_when(age_days < 90 ~ 1,
                                  age_days > 90 ~ 0))

operators %<>% select(c(operator, new))
```

```{r}
bad_payers <- left_join(bad_payers, operators)
```

```{r}
# Defining whether they bad_payer or not
bad_payers[is.na(bad_payers)] <- 0

bad_payers %<>% mutate(bad_payer = case_when(new == 1 & m2 >= 0 & m3 >= 0 ~ "Yes",
                                  new == 0 & m3 > 100 ~ "Yes",
                                  TRUE ~ "No"))

bad_payers %<>% select(c(operator, bad_payer))
```

```{r}
brand_payers <- read.csv("Brands.csv")

brand_payers %<>% rename(operator = Company)

brand_payers %<>% subset(operator!="")

bad_payers <- left_join(brand_payers, bad_payers)

bad_payers[is.na(bad_payers)] <- "No"

bad_payers %<>% rename(brand = Brand.Name)

bad_payers %<>% select(c(brand, bad_payer))
```

```{r}
bad_payers$brand <- tolower(bad_payers$brand)

bad_payers$brand <- gsub(" ", "", bad_payers$brand, fixed = TRUE)
bad_payers$brand <- gsub(".", "", bad_payers$brand, fixed = TRUE)

bad_payers <- rename(bad_payers, name = brand)

bad_payers %<>% distinct(name, .keep_all = TRUE)
```

________________________________________________________________________________

# Loading data for page specific metrics and if they have deal present

```{r}

sql3 <- "SELECT DISTINCT

brandid,
marketid,
ARRAY_TO_STRING(games, ',') AS Games,
ARRAY_TO_STRING(paymentproviders, ',') AS Paymentproviders,
payment.payNPlay AS paynplayCM,
details.localLanguage,

CASE WHEN (details.localLanguage) IS TRUE THEN '1' ELSE '0' END AS Local,
CASE WHEN (payment.payNPlay) IS TRUE THEN '1' ELSE '0' END AS PayNPlay,
CASE WHEN 'Zimpler' IN UNNEST(paymentproviders)THEN '1' ELSE '0' END AS Zimpler,
CASE WHEN 'Brite' IN UNNEST(paymentproviders)THEN '1' ELSE '0' END AS Brite,
CASE WHEN 'Trustly' IN UNNEST(paymentproviders)THEN '1' ELSE '0' END AS Trustly,
CASE WHEN 'Visa' IN UNNEST(paymentproviders)THEN '1' ELSE '0' END AS Visa,
CASE WHEN 'Paypal' IN UNNEST(paymentproviders)THEN '1' ELSE '0' END AS Paypal,
CASE WHEN 'Siirto' IN UNNEST(paymentproviders)THEN '1' ELSE '0' END AS Siirto,
CASE WHEN 'Euteller' IN UNNEST(paymentproviders)THEN '1' ELSE '0' END AS Euteller,
CASE WHEN 'SIRU Mobile' IN UNNEST(paymentproviders)THEN '1' ELSE '0' END AS SIRU,
CASE WHEN 'Betting' IN UNNEST(games)THEN '1' ELSE '0' END AS Betting,
CASE WHEN 'Bingo' IN UNNEST(games)THEN '1' ELSE '0' END AS Bingo,
CASE WHEN 'Live casino' IN UNNEST(games)THEN '1' ELSE '0' END AS Casino

FROM `thunderkick-prod.casinomeister.latestData_casinomeister_dataByCountries` 

"

globaldata <- dbGetQuery(con, sql3)

globaldata$brandid <- gsub("iiwildcasino", "iwildcasino", globaldata$brandid)

globaldatatesting <- globaldata

globaldata$brandid <- gsub("-", "", globaldatatesting$brandid, fixed = TRUE)

globaldata$brandid <- gsub("luckom", "luckcom", globaldata$brandid, fixed = TRUE)
```

```{r}
globaldatatesting %<>% select(!(c(Games, Paymentproviders, paynplayCM, localLanguage)))
```

## Adding whether a deal is present in the GEO for either site or paid position

```{r}
sql4 <- "SELECT DISTINCT

channel.slug AS channel,
brand.slug AS brandid,
market.slug AS marketid

FROM `thunderkick-prod.affiliate_meister_data.latestData`

WHERE channel.slug = 'site' OR channel.slug = 'paid-position' 
  AND status.id = 1
"

deal_geo <- dbGetQuery(con, sql4)

deal_geo %<>% mutate(marketid = case_when(marketid == "se" ~ "row",  TRUE ~ marketid))

deal_geo$brandid <- gsub("luckom", "luckcom", deal_geo$brandid, fixed = TRUE)

deal_geo$brandid <- gsub("sisu-3972", "sisu", deal_geo$brandid, fixed = TRUE)

globaldata <- left_join(globaldata, deal_geo)

globaldata %<>% subset(marketid == "fi" | marketid == "de" | marketid == "row" | marketid == "ro") 

globaldata %<>% subset(channel == "paid-position" | channel == "site")

globaldatatesting$deal <- 1 # Maybe not necessary check later

globaldata %<>% select(!(c(Games, Paymentproviders)))
```


_________________________________________________________________

CM DATA AUTOMATAED!!!


```{r}
sql5 <- "SELECT DISTINCT 

casinoId,
flair,
positionNumber,
siteid,
type,
campaignPeriodMonth AS month,
campaignPeriodYear AS year,
listType

FROM `thunderkick-prod.casinomeister.latestData_campaignMeister`
  WHERE status = 'Active'
  AND campaignPeriodYear > 2021"

pos_extract <- dbGetQuery(con, sql5)
```

# Loading positions (Positions) ATM Manual data download

```{r}
# Adjusting variables for merging
pos_new <- pos_extract

pos_new <- rename(pos_new, name = casinoId)
pos_new <- rename(pos_new, Site = siteid)
pos_new <- rename(pos_new, Position = positionNumber)
pos_new <- rename(pos_new, ListType = listType)
pos_new <- rename(pos_new, Flair = flair)

pos_new$name <- gsub("luckom", "luckcom", pos_new$name, fixed = TRUE)

# Current pos

pos_new$my <- paste(pos_new$month, pos_new$year) 

pos_new %<>% select(!(c(month, year)))

pos_new$my <- as.yearmon(pos_new$my)
pos_new$my <- as.Date(pos_new$my)

## Extracting current month from Sys.Date()
sys_date <- format(Sys.Date(),"%Y-%m")
sys_date <- data.frame(sys_date)
sys_date$day <- "-01"
sys_date <- paste(sys_date, collapse="")
sys_date <- data.frame(sys_date)
sys_date$sys_date %<>% as.Date()

pos_new %<>% subset(my == sys_date)

pos_new %<>% unique()

# Sold pos

sold_pos_main <- pos_extract

sold_pos_main <- rename(sold_pos_main, name = casinoId)
sold_pos_main <- rename(sold_pos_main, Site = siteid)
sold_pos_main <- rename(sold_pos_main, Position = positionNumber)
sold_pos_main <- rename(sold_pos_main, ListType = listType)
sold_pos_main <- rename(sold_pos_main, Flair = flair)

sold_pos_main$name <- gsub("luckom", "luckcom", sold_pos_main$name, fixed = TRUE)

sold_pos_main$my <- paste(sold_pos_main$month, sold_pos_main$year) 

sold_pos_main %<>% select(!(c(month, year)))

sold_pos_main$my <- as.yearmon(sold_pos_main$my)
sold_pos_main$my <- as.Date(sold_pos_main$my)

## Extracting next month from Sys.Date()
sys_date <- format(Sys.Date(),"%Y-%m")
sys_date <- data.frame(sys_date)
sys_date$day <- "-01"
sys_date <- paste(sys_date, collapse="")
sys_date <- data.frame(sys_date)
sys_date$sys_date %<>% as.Date()


sys_date$sys_date <- sys_date$sys_date %m+% period("1 month")

sold_pos_main %<>% subset(my == sys_date)

sold_pos_main %<>% unique()
```


# Account and deal information

```{r}
sql6 <- "SELECT DISTINCT
affiliateSoftwareAccount.loginUsername AS account,
brand.slug AS name,
market.slug AS market,
cpa,
revshare,
baseline

 FROM `thunderkick-prod.affiliate_meister_data.latestData` 
  WHERE channel.slug = 'site'
  AND market.slug = 'fi' OR market.slug = 'de' OR market.slug = 'row' OR market.slug = 'ro'"

deal_account <- dbGetQuery(con, sql6)

# Adjusting wrong slug naming

deal_account$name <- gsub("luckom", "luckcom", deal_account$name, fixed = TRUE)
deal_account$name <- gsub("winbet-3935", "winbet", deal_account$name, fixed = TRUE)
deal_account$name <- gsub("betano", "betano.ro", deal_account$name, fixed = TRUE)
```

________________________________________________________________________________